Generate data for multispecies modeling, including diet!

### 2020-09-04 NOBAmsdiets.Rmd
testing code works function doesnt

detaileddiettest <- load_detailed_diet_comp(here("atlantisoutput",
                                                 "NOBA_march_2020"), 
                           "NOBADetDiet.gz", 
                           fgs = fgs)

@@

ms_detaileddiet <- detaileddiettest %>%
  filter(species %in% sppsubset$Name)

>>>>

diet <- data.table::fread(file.path(here("atlantisoutput",
                                                  "NOBA_march_2020"), 
                                                "NOBADetDiet.gz"))

  # remove all 0 prey rows--done with awk statement first, file is too big for R to do this
  #diet <- diet[as.logical(rowSums(diet[,-c(1:5)] != 0)), ]

  # SKG June 2020: changing to the other way around. more new models now,
  # only one diet function to change, and "Predator" seems clearer for users.
  if(length(grep("Group",colnames(diet)))>0)
    colnames(diet) <- gsub("Group","Predator",colnames(diet))

  # Change column order--NOT DATA TABLE SAFE
  #diet <- diet[, c("Predator", "Cohort", "Time", "Box", "Layer",
  #  names(diet)[which(!names(diet) %in% c("Predator", "Cohort", "Time", "Box", "Layer"))])]

  data.table::setcolorder(diet, c("Predator", "Cohort", "Time", "Box", "Layer"))

  #should do the same thing faster
  #diet <- diet[as.logical(abs(as.matrix(diet[,-c(1:5)])) %*% rep(1L,ncol(diet[,-c(1:5)]))), ]

  # dataframe
  #diet <- as.data.frame(diet)

  diet <- data.table::melt(diet, id = 1:5,
               variable.name="prey",
               value.name = "dietcomp")

  # Get rid of 0 dietcomp rows to make manageable size
  diet <- diet[dietcomp>0]
  #diet <- filter(diet, dietcomp>0)

  # Change species acronyms to actual names.
  species_names <- fgs[, c("Name", "Code")]
  diet$species <- species_names$Name[match(diet$predator, species_names$Code)]
  diet$prey <- species_names$Name[match(diet$prey, species_names$Code)]
  #diet <- diet[, -which(colnames(diet) == "predator")]

  #fix cohort to agecl
  # diet <- diet %>%
  #   dplyr::mutate(agecl = cohort + 1)
  diet <- diet[, agecl := cohort + 1]

  # drop redundant columns and reorder NOT DATA TABLE SAFE
  #diet <- diet[,c("species", "agecl", "time.days", "box", "layer", "prey", "dietcomp")]

  #leave layer info for now, this is a load function

  #does the Update column matter? this assumes it doesn't
  #in SETAS_Example, it doesn't make extra comps

  dietcompwt <- data.frame(species = diet$species,
                         agecl = diet$agecl,
                         time.days = diet$time.days,
                         polygon = diet$box,
                         layer = diet$layer,
                         atoutput = diet$dietcomp,
                         prey = diet$prey)

# function not working so test piecewise again
# detaileddiettest <- load_detailed_diet_comp(here("atlantisoutput",
#                                                  "NOBA_march_2020"), 
#                            "NOBADetDiet.gz", 
#                            fgs = fgs)

@@

Still having problems with the function after editing

```{r detdiettest, eval=FALSE}

# still not working but works line by line
detdiet <- load_detailed_diet_comp(here("atlantisoutput","NOBA_march_2020"), 
                                   "NOBADetDiet.gz", 
                                   fgs = fgs)

ms_detaileddiet <- detdiet %>%
  filter(species %in% sppsubset$Name)
